---
title: "About"
author: "Alyson Givre"
date: "4/25/2021"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

All data used in this application was extracted from the [FBI Uniform Crime Reporting (UCR) Program](https://www.fbi.gov/services/cjis/ucr). The program has been collecting data since 1930 from over 18,000 law enforcement agencies.

This application includes a subset of this data from 2010 to 2019 focusing on the violent crimes committed broken down by state. Below is a further subset of the data which includes the columns:
  * State
  * Population - Total population of the state
  * ViolentCrime - Total number of violent crimes committed
  * Year
  * CrimeRate - Number of violent crimes committed per 100,000 people
  * Legalized - The legalization status of recreational cannabis

```{r display-state, results='asis'}
source('../process-data.R')

fbi_state <- get_state_data('../data/')
fbi_state[, c(1, 4, 5, 14, 15, 16)] %>%
  kbl() %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")
```


Another subset this application looks at is the same information, focused on the metropolitan areas within each state. The data below contains the following columns:

  * State
  * Population - Total population within the state's metropolitan areas
  * ViolentCrime - Total number of violent crimes committed within the state's metropolitan areas
  * Year
  * CrimeRate - Number of violent crimes committed per 100,000 people
  * Legalized - The legalization status of recreational cannabis

```{r display-metro, results='asis'}
source('../process-data.R')

fbi_state <- get_metro_data('../data/')
fbi_state[, c(1, 4, 5, 14, 15, 16)] %>%
  kbl() %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")
```



